---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# buoydata

<!-- badges: start -->
[![gh-pages](https://github.com/NOAA-EDAB/buoydata/actions/workflows/pkgdown.yml/badge.svg)](https://github.com/NOAA-EDAB/buoydata/actions/workflows/pkgdown.yml)
[![R-CMD-check](https://github.com/NOAA-EDAB/buoydata/actions/workflows/check-standard.yml/badge.svg)](https://github.com/NOAA-EDAB/buoydata/actions/workflows/check-standard.yml)
[![gitleaks](https://github.com/NOAA-EDAB/buoydata/actions/workflows/secretScan.yml/badge.svg)](https://github.com/NOAA-EDAB/buoydata/actions/workflows/secretScan.yml)

<!-- badges: end -->

The goal of `buoydata` is to easily download and process buoy data hosted by National Data Buoy Center. Note: the [rnoaa](https://github.com/ropensci/rnoaa) package also has functions to get buoy data. The difference is that (in [rnoaa](https://github.com/ropensci/rnoaa)) only one years worth of data can be downloaded at any time from a single buoy. 

`buoydata` downloads all of the buoys data from ERDDAP. In addition the lazily loaded station description data provided with the package combines many more attributes (than [rnoaa](https://github.com/ropensci/rnoaa)) by which to filter. 

*Date of most recent data pull: `r strsplit(as.character(file.info(here::here("data-raw","datapull.txt"))$ctime)," ")[[1]][1]`*

## Installation

``` r
pak::pak("NOAA-EDAB/buoydata")
```

## Example

Find all buoys located between latitude [41,43] and longitude [-71,-67] with a time series of at least 20 years. Then pull and process data from a single buoy. 

``` {r, eval=TRUE}
library(buoydata)

buoydata::buoyDataWorld |> 
  dplyr::filter(LAT > 41,LAT < 43) |> 
  dplyr::filter(LON > -71, LON < -69) |> 
  dplyr::filter(nYEARS >= 20)
```


Lets pull the sea surface temperature (variable name, wtmp) from buoy 44018 - `r buoydata::buoyDataWorld |> dplyr::filter(ID == 44018) |> dplyr::pull(STATION_LOC)`

``` {r, eval = TRUE, echo = TRUE}
buoy_data <- get_buoy_data(buoyid="44018", var = "wtmp")
```

Then plot the data

```{r plotData, echo = TRUE, eval = TRUE}
 p <- ggplot2::ggplot(buoy_data) +
   ggplot2::geom_line(ggplot2::aes(x=time,y=wtmp)) + 
   ggplot2::ylab("Sea Surface Temp (Celcius)") +
   ggplot2::xlab("")
print(p)
```


## Contact

| [andybeet](https://github.com/andybeet)        
| ----------------------------------------------------------------------------------------------- 
| [![andybeet avatar](https://avatars1.githubusercontent.com/u/22455149?s=100&v=4)](https://github.com/andybeet) | 



#### Legal disclaimer

*This repository is a scientific product and is not official
communication of the National Oceanic and Atmospheric Administration, or
the United States Department of Commerce. All NOAA GitHub project code
is provided on an ‘as is’ basis and the user assumes responsibility for
its use. Any claims against the Department of Commerce or Department of
Commerce bureaus stemming from the use of this GitHub project will be
governed by all applicable Federal law. Any reference to specific
commercial products, processes, or services by service mark, trademark,
manufacturer, or otherwise, does not constitute or imply their
endorsement, recommendation or favoring by the Department of Commerce.
The Department of Commerce seal and logo, or the seal and logo of a DOC
bureau, shall not be used in any manner to imply endorsement of any
commercial product or activity by DOC or the United States Government.*

